---
title: Analysis of Standard Urban Model (SUM)
author: Derek Ding 
date: "`r Sys.Date()`" 
output:
  html_document:
    df_print: paged
    code_folding: show
---

# SUM Analysis for UK Cities

## 0. Project bjective:
This project aims to analyze the applicability of SUM to certain UK cities with GIS
data, socio-economic data, travel demand/behaviour data etc.

Other contextual data: 
- [Consumer Data Research Centre (CDRC) in the United Kingdom](maps.cdrc.ac.uk/)
- [Commute Data](www.commute.datashine.org.uk/)
- [Interactive maps and visualizations of various types of data for the United Kingdom](www.datashine.org.uk/) 
- [Interactive maps and visualizations of various types of data for the United Kingdom Scotland](www.scotland.datashine.org.uk)
- [Carbon Emission Data](www.carbon.place)
- [Open Street Map](www.openstreetmap.org) 
- [England-wide data: ](https://www.centreforcities.org/data/)

- Read in global [gender inequality](https://hdr.undp.org/data-center/documentation-and-downloads) data

## 1. Load libraries and Import Data

In this assignment we will use the following libraries:

### 1.1 Libraries
```{r echo= TRUE, error=TRUE}
library(sf)
library(tidyverse)
# library(dplyr)
library(shiny)
library(tmap)
library(tmaptools)
library(readxl)
library(sf)
library(here)
library(leaflet)
library(raster)
library(dplyr)
library(terra)
library(countrycode)
```


```{r echo= TRUE, error=TRUE}

glasgow_rent_v_dist <- read.csv("D:/OneDrive - University College London/T1/CASA0001/0. assessments/Assignment 1/data/dataglasgow_rent_dist2.csv")
```



```{r echo= TRUE, error=TRUE}
glasgow_rent_v_dist
```
2 Beds Flats:

```{r echo= TRUE, error=TRUE}
glg.flats <- glasgow_rent_v_dist[glasgow_rent_v_dist$Type == 'F',]
glg.houses <- glasgow_rent_v_dist[glasgow_rent_v_dist$Type == 'H',]

#glg.flats
#glg.houses
```

```{r echo= TRUE, error=TRUE}
library(ggplot2)
```
Change the room number, as it is the integer now, the ggplot function does not 
take that as input
```{r echo= TRUE, error=TRUE}
glg.flats <- glg.flats %>%
  mutate(Bed_type = case_when(
    Beds == 1 ~ "1 bedrooms",
    Beds == 2 ~ "2 bedrooms",
    Beds == 3 ~ "3 bedrooms",
    Beds == 4 ~ "4 bedrooms",
    Beds == 5 ~ "5 bedrooms",
    Beds == 6 ~ "6 bedrooms"
    ))
```

```{r echo= TRUE, error=TRUE}

```



Plot the flats
```{r echo= TRUE, error=TRUE}
ggplot(glg.flats, 
       aes(x = distance_to_town_centre, 
           y = rent, 
           color = Bed_type,
           shape = Bed_type)) +
  geom_smooth(method = "glm")+
  #geom_smooth(method = "loess")+
  #geom_jitter(height = 0.05)+
  #binomial_smooth()+
  #geom_smooth(method=lm, se=FALSE, fullrange=TRUE) +
  geom_point() +
  labs(x="Distance to city centre (KM)", 
       y = "Rent",
       fill = "Model") +
  ggtitle("Distance and Rent Relation for Flats in Glasgow") +
  theme(plot.title = element_text(lineheight=3,
                                   hjust = 0.5, # Plot title in the middle
                                   face="bold", # bold
                                   color="black",size=16) # title
         )+
  theme( legend.position = "right", 
         legend.background = element_rect(fill="lightyellow",
                                  size=0.3, linetype="solid", 
                                  colour ="black"))
```



Now do the same for the houses:


```{r echo= TRUE, error=TRUE}
glg.houses <- glg.houses %>%
  mutate(Bed_type = case_when(
    Beds == 1 ~ "1 bedrooms",
    Beds == 2 ~ "2 bedrooms",
    Beds == 3 ~ "3 bedrooms",
    Beds == 4 ~ "4 bedrooms",
    Beds == 5 ~ "5 bedrooms",
    Beds == 6 ~ "6+ bedrooms",
    Beds == 10 ~ "6+ bedrooms",
    Beds == 8 ~ "6+ bedrooms",
    Beds == 7 ~ "6+ bedrooms",
    Beds == 9 ~ "6+ bedrooms"
    ))
```



```{r echo= TRUE, error=TRUE}
ggplot(glg.houses, 
       aes(x = distance_to_town_centre, 
           y = rent, 
           color = Bed_type,
           shape = Bed_type)) +
  #geom_smooth(method=lm, se=FALSE, fullrange=TRUE) +
  #geom_smooth(method = "glm")+
  geom_smooth(method = "loess")+
  geom_point() +
  labs(x="Distance to city centre (KM)", 
       y = "Rent",
       fill = "Model") +
  ggtitle("Distance and Rent Relation for Houses in Glasgow") +
  theme(plot.title = element_text(lineheight=3,
                                   hjust = 0.5, # Plot title in the middle
                                   face="bold", # bold
                                   color="black",size=16) # title
         )+
  theme( legend.position = "right", 
         legend.background = element_rect(fill="lightyellow",
                                  size=0.3, linetype="solid", 
                                  colour ="black"))
```


```{r echo= TRUE, error=TRUE}

```



```{r echo= TRUE, error=TRUE}

```


```{r echo= TRUE, error=TRUE}

```



```{r echo= TRUE, error=TRUE}

```


```{r echo= TRUE, error=TRUE}

```



```{r echo= TRUE, error=TRUE}

```


```{r echo= TRUE, error=TRUE}

```



```{r echo= TRUE, error=TRUE}

```


```{r echo= TRUE, error=TRUE}

```




```{r echo= TRUE, error=TRUE}

```


```{r echo= TRUE, error=TRUE}

```



```{r echo= TRUE, error=TRUE}

```


```{r echo= TRUE, error=TRUE}

```





```{r echo= TRUE, error=TRUE}

```


```{r echo= TRUE, error=TRUE}

```



```{r echo= TRUE, error=TRUE}

```


```{r echo= TRUE, error=TRUE}

```





















